Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-04-11 ms.tex
cleaning up some wording in molecular emission discussion

We must apply the appropriate unit conversions to the $6.1'$ Type 3 CO
map before we can subtract it from the \PLANCK~intensity maps, which at the
frequencies of interest have native units of $K_{CMB}$. The Type 3 CO map
is provided in units of K$_{RJ}$ km/s of J=1$\rightarrow$0 emission. 
To convert this quantity to $K_{CMB}$, we assume that all of the CO emission 
arises from the $^{12}$CO isotope, and derived the \PLANCK-observed CO 
intensity in units of $K_{CMB}$ as follows:

>>>>

We must apply the appropriate unit conversions to the $6.1'$ Type 3 CO
map before subtracting it from the \PLANCK~intensity maps, which have native 
units of $K_{CMB}$ at the frequencies of interest. The Type 3 CO map is 
provided in units of K$_{RJ}$ km/s of J=1$\rightarrow$0 emission. To convert 
this quantity to $K_{CMB}$, we assume that all of the CO emission arises from 
the $^{12}$CO isotope, and derived the \PLANCK-observed CO intensity in units 
of $K_{CMB}$ as follows:
